### 2022-06-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@348041f6d355b99d641733ea19c6c0e367cf761b 🚀

\hypertarget{coevolutionary-regimes-create-distinct-hotspots-of-betacoronavirus-biodiversity}{%
\subsection{Coevolutionary regimes create distinct hotspots of
betacoronavirus
biodiversity}\label{coevolutionary-regimes-create-distinct-hotspots-of-betacoronavirus-biodiversity}}

>>>>

\hypertarget{hotspots-of-bat-and-betacoronavirus-biodiversity-are-distinct}{%
\subsection{Hotspots of bat and betacoronavirus biodiversity are
distinct}\label{hotspots-of-bat-and-betacoronavirus-biodiversity-are-distinct}}
